Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2021-12-22 Manuscript/FLPhish(Trans).tex
algorithm->rule

\subsection{Byzantine Defense Methods in Federated Learning}
Byzantine-robust schemes are very important for FL to enhance its security. Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL. Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine clients. 
For example, in 2017, Chen \textit{et al}. Krum developed an approach \cite{ref_12_defense}. Krum selects one client's update as a global model based on a square-distance score in each iteration. 
In the same year, Blanchard \textit{et al}. proposed two Byzantine-tolerant FL aggregation algorithms Trimmed mean and Median \cite{ref_16_defense}. Trimmed Mean considers each parameter of the model update individually. Trimmed Mean sorts the parameter of the model updates collected. Median sorts the values of each parameter of all local model updates as well. And it considers the median value of each parameter as the value of the parameter in the global model update. 
In 2018, Chen \textit{et al.} designed an approach Draco to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
In 2019, Zeno uses a ranking-based preference mechanism \cite{ref_15_defense}. The server computes a score for each client by using the stochastic zero-order oracle. Then Zeno presents a ranking list of clients based on the estimated descent of the loss function and the magnitudes. At last, Zeno computes the global model update by aggregating the clients with the highest scores. 
In 2020, SLSGD developed by Xie \textit{et al.} also uses trimmed mean as the robust aggregation rules for Byzantine-robust FL \cite{ref_14_defense}. 
In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}. In each iteration, the server calculates a trust score for each client at first and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update. The client with a trust score lower than the threshold is considered a malicious client.
In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}. PEFL takes advantage of homomorphic encryption to protect the privacy of the clients. Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.

\subsection{Reputation Mechanism in Information Security}
The reputation mechanism is valued as a way to measure an entity's performance in a long term, such as in an online social network \cite{ref_27_reputation}, and in a smart grid system, \cite{ref_41_reputation, ref_44_reputation}.
In 2012, Das \textit{et al.} first presented a dynamic trust computation model called SecuredTrust. This framework is used to distribute the workload and deal with the altering behavior of malicious clients \cite{ref_48_reputation}.
In 2015, Zhu \textit{et al.} proposed an authenticated trust and reputation calculation and management system in wireless sensor network and cloud computing to calculate and manage trust and reputation of the service of CSP and SNP \cite{ref_47_reputation}.
In 2018, Lei \textit{et al.} presented a Reputation-based Byzantine Fault Tolerance algorithm that incorporates a reputation model to evaluate the performance of each node in the blockchain system \cite{ref_25_reputation}. The nodes get lower discourse rights and reputation in the voting process if any malicious behavior is detected by the system. Furthermore, they presented a reputation-based primary change scheme. The node with a higher reputation would get greater opportunities to generate new valid blocks, which reduces the security risk of the system.
In 2020, Chouikhi \textit{et al.} built a model for reputation computing and a credibility model to enhance network efficiency \cite{ref_23_reputation}. They used the reputation score or value to measure the behavior of a vehicle towards other vehicles and network services. And the credibility of vehicles is used to determine the accuracy of a reputation score offered by a vehicle. 
In the same year, Wen \textit{et al.} proposed a Dirichlet reputation-based scheme and adopt the reputation score to select a trustworthy Helper as a friendly jammer in a wireless cooperative system (WCS) \cite{ref_24_reputation}. Furthermore, they developed an artificial noise detection method with multiple thresholds. They provided ratings with multiple graded levels. In the Dirichlet reputation-based scheme, the graded ratings were directly expressed and reflected in the derived reputation scores.
In 2021, Liang \textit{et al.} presented a Markov-based reputation scheme in an intrusion detection system. The Hidden Generalized Mixture Transition Distribution (HgMTD) model, namely RS-HgMTD, is developed to assist each vehicle in the VANET to measure the creditworthiness of its neighbor vehicles \cite{ref_46_reputation}.

@@

\section{Proposed FLPhish Scheme}
In this section, we show the proposed FLPhish scheme including the Ensemble Federated Learning, the phishing mechanism, the reputation mechanism, and the aggregation algorithms.

@@

\subsection{Aggregation Algorithms}
Based on our reputation mechanism, we propose our Byzantine-tolerant aggregation algorithms: FLPhish-threshold and FLPhish-weight.
\subsubsection{{FLPhish-threshold}}
FLPhish-threshold functions as the aggregation rules identify the clients whose reputation is lower than the reputation threshold. Then the server discards the Byzantine clients and aggregates the global model using the survived clients' updates. Server identifies the client ${c_{i}}$ whose reputation is lower than the threshold $\tau$ as Byzantine clients, and given them a aggregation weight as
\begin{equation}
  \omega_{i}=\begin{cases}
    1 & \text{ if } x\geq \tau \\ 
    0 & \text{ if } x< \tau 
    \end{cases}.
\end{equation} 
The aggregated knowledge is given by
\begin{equation}
  \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times \omega_{i},
\end{equation}
\begin{equation}
  \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
\end{equation} 
\subsubsection{{FLPhish-weight}}
Unlike FLPhish-threshold, FLPhish-weight does not discard the potential Byzantine clients' updates. On the contrary, it enables the Byzantine clients to participate the aggregation using its reputation value as the aggregation weight. Due to our reputation mechanism, the Byzantine clients are offered a low value of reputation, so it has a lower influence on aggregation.
Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$, the prediction results is 
  \begin{equation}
    \mathbf{k_i^t}=\begin{vmatrix}
      p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
      \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
      p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
      \end{vmatrix},
  \end{equation}
  FLPhish-weight computes the aggregated knowledge, which is
    \begin{equation}
    \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times x_{i}.
  \end{equation}
  Then the server $s$ uses the aggregated knowledge $\mathbf{\hat{k}^t}$ to get the labels
  \begin{equation}
    \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
  \end{equation} 
In a word, FLPhish-weight does not identify the Byzantine clients but treats the clients with a low reputation as `bad' clients and give them lower weight.

>>>>

\subsection{Byzantine Defense Methods in Federated Learning}
Byzantine-robust schemes are very important for FL to enhance its security. Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL. Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine clients. 
For example, in 2017, Chen \textit{et al}. Krum developed an approach \cite{ref_12_defense}. Krum selects one client's update as a global model based on a square-distance score in each iteration. 
In the same year, Blanchard \textit{et al}. proposed two Byzantine-tolerant FL aggregation rules Trimmed mean and Median \cite{ref_16_defense}. Trimmed Mean considers each parameter of the model update individually. Trimmed Mean sorts the parameter of the model updates collected. Median sorts the values of each parameter of all local model updates as well. And it considers the median value of each parameter as the value of the parameter in the global model update. 
In 2018, Chen \textit{et al.} designed an approach Draco to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
In 2019, Zeno uses a ranking-based preference mechanism \cite{ref_15_defense}. The server computes a score for each client by using the stochastic zero-order oracle. Then Zeno presents a ranking list of clients based on the estimated descent of the loss function and the magnitudes. At last, Zeno computes the global model update by aggregating the clients with the highest scores. 
In 2020, SLSGD developed by Xie \textit{et al.} also uses trimmed mean as the robust aggregation rules for Byzantine-robust FL \cite{ref_14_defense}. 
In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}. In each iteration, the server calculates a trust score for each client at first and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update. The client with a trust score lower than the threshold is considered a malicious client.
In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}. PEFL takes advantage of homomorphic encryption to protect the privacy of the clients. Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.

\subsection{Reputation Mechanism in Information Security}
The reputation mechanism is valued as a way to measure an entity's performance in a long term, such as in an online social network \cite{ref_27_reputation}, and in a smart grid system, \cite{ref_41_reputation, ref_44_reputation}.
In 2012, Das \textit{et al.} first presented a dynamic trust computation model called SecuredTrust. This framework is used to distribute the workload and deal with the altering behavior of malicious clients \cite{ref_48_reputation}.
In 2015, Zhu \textit{et al.} proposed an authenticated trust and reputation calculation and management system in wireless sensor network and cloud computing to calculate and manage trust and reputation of the service of CSP and SNP \cite{ref_47_reputation}.
In 2018, Lei \textit{et al.} presented a Reputation-based Byzantine Fault Tolerance rule that incorporates a reputation model to evaluate the performance of each node in the blockchain system \cite{ref_25_reputation}. The nodes get lower discourse rights and reputation in the voting process if any malicious behavior is detected by the system. Furthermore, they presented a reputation-based primary change scheme. The node with a higher reputation would get greater opportunities to generate new valid blocks, which reduces the security risk of the system.
In 2020, Chouikhi \textit{et al.} built a model for reputation computing and a credibility model to enhance network efficiency \cite{ref_23_reputation}. They used the reputation score or value to measure the behavior of a vehicle towards other vehicles and network services. And the credibility of vehicles is used to determine the accuracy of a reputation score offered by a vehicle. 
In the same year, Wen \textit{et al.} proposed a Dirichlet reputation-based scheme and adopt the reputation score to select a trustworthy Helper as a friendly jammer in a wireless cooperative system (WCS) \cite{ref_24_reputation}. Furthermore, they developed an artificial noise detection method with multiple thresholds. They provided ratings with multiple graded levels. In the Dirichlet reputation-based scheme, the graded ratings were directly expressed and reflected in the derived reputation scores.
In 2021, Liang \textit{et al.} presented a Markov-based reputation scheme in an intrusion detection system. The Hidden Generalized Mixture Transition Distribution (HgMTD) model, namely RS-HgMTD, is developed to assist each vehicle in the VANET to measure the creditworthiness of its neighbor vehicles \cite{ref_46_reputation}.

@@

\section{Proposed FLPhish Scheme}
In this section, we show the proposed FLPhish scheme including the Ensemble Federated Learning, the phishing mechanism, the reputation mechanism, and the aggregation rules.

@@

\subsection{Aggregation Rules}
Based on our reputation mechanism, we propose our Byzantine-tolerant aggregation rules: FLPhish-threshold and FLPhish-weight.
\subsubsection{{FLPhish-threshold}}
FLPhish-threshold functions as the aggregation rules identify the clients whose reputation is lower than the reputation threshold. Then the server discards the Byzantine clients and aggregates the global model using the survived clients' updates. Server identifies the client ${c_{i}}$ whose reputation is lower than the threshold $\tau$ as Byzantine clients, and given them a aggregation weight as
\begin{equation}
  \omega_{i}=\begin{cases}
    1 & \text{ if } x\geq \tau \\ 
    0 & \text{ if } x< \tau 
    \end{cases}.
\end{equation} 
The aggregated knowledge is given by
\begin{equation}
  \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times \omega_{i},
\end{equation}
\begin{equation}
  \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
\end{equation} 
\subsubsection{{FLPhish-weight}}
Unlike FLPhish-threshold, FLPhish-weight does not discard the potential Byzantine clients' updates. On the contrary, it enables the Byzantine clients to participate the aggregation using its reputation value as the aggregation weight. Due to our reputation mechanism, the Byzantine clients are offered a low value of reputation, so it has a lower influence on aggregation.
Give a reputation list $R=\left | x_{1},x_{1},x_{1},\cdots ,x_{n-1},x_{n} \right |$, the prediction results is 
  \begin{equation}
    \mathbf{k_i^t}=\begin{vmatrix}
      p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
      \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
      p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
      \end{vmatrix},
  \end{equation}
  FLPhish-weight computes the aggregated knowledge, which is
    \begin{equation}
    \mathbf{\hat{k}^t}=\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i\times x_{i}.
  \end{equation}
  Then the server $s$ uses the aggregated knowledge $\mathbf{\hat{k}^t}$ to get the labels
  \begin{equation}
    \mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t}).
  \end{equation} 
In a word, FLPhish-weight does not identify the Byzantine clients but treats the clients with a low reputation as `bad' clients and give them lower weight.
